### 2017-03-10 docs/ms_communitySynchrony_ForECOLOGY_PREPRINT.tex
adds proof corrections to preprint version for EU posting

%%\usepackage{lineno}
%%\linenumbers
\usepackage{todonotes}
\usepackage{rotating}
\usepackage{color, soul}
\usepackage{times}
\usepackage[document]{ragged2e}
\usepackage{titlesec}
\titleformat{\section}{\normalsize\sc\centering}{\thesection}{1em}{}
\titleformat{\subsection}{\normalsize\it\centering}{\thesubsection}{1em}{}
\titleformat*{\paragraph}{\normalsize\it}

@@

\begin{center}
\large{\textbf{Environmental responses, not species interactions, determine synchrony of dominant species in semiarid grasslands}}

@@

\begin{abstract}
\normalsize
\emph{Abstract.}\hspace{1em}Temporal asynchrony among species helps diversity to stabilize ecosystem functioning, but identifying the mechanisms that determine synchrony remains a challenge.
Here, we refine and test theory showing that synchrony depends on three factors: species responses to environmental variation, interspecific interactions, and demographic stochasticity. We then conduct simulation experiments with empirical population models to quantify the relative influence of these factors on the synchrony of dominant species in five semiarid grasslands.
We found that the average synchrony of per capita growth rates, which can range from 0 (perfect asynchrony) to 1 (perfect synchrony), was higher when environmental variation was present (0.62) rather than absent (0.43).
Removing interspecific interactions and demographic stochasticity had small effects on synchrony. 
For the dominant species in these plant communities, where species interactions and demographic stochasticity have little influence, synchrony reflects the covariance in species responses to the environment.

@@

While existing theory has identified
environmental responses, species interactions, and demographic stochasticity as the drivers of the temporal synchrony,
we do not have a simple expression to predict synchrony in a particular
community with all factors operating simultaneously. However, we can
derive analytical predictions for species synchrony under special
limiting cases. The limiting case predictions we derive serve as
baselines to help us interpret results from empirically-based
simulations (described below). We focus on synchrony of per capita
growth rates, rather than abundances, because growth rates represent the
instantaneous response of species to the environment and competition,
and are less susceptible to the legacy effects of drift and disturbance
(Loreau and {{de Mazancourt}} 2008). We present equivalent results for
synchrony of species abundances in the Appendix S1, and show that they
lead to the same overall conclusions as synchrony of per capita growth
rates.

@@

\noindent where \(\sigma_{r_{i}}\) is the temporal
standard deviation of species \emph{i'}s per capita
population growth rate (\(r_i\)) and \(\sigma^{2}_{T}\) is the temporal
variance of the aggregate community-level growth rate. \(\phi\) ranges
from 0 at perfect asynchrony to 1 at perfect synchrony (Loreau and {{de
Mazancourt}} 2008). We use the same equation to calculate observed
synchrony of species' percent cover, which we present to relate our
results to previous findings, even though we focus on synchrony of
growth rates in our model simulations (see below).

@@

Vital rate regressions are the building blocks of our dynamic models: an
integral projection model (IPM) and an individual-based model (IBM). We
followed the approach of Chu and Adler (2015) to fit statistical models
for survival, growth, and recruitment (see Appendix S1 for full
details). We modeled survival probability of each genet as function of
genet size, temporal variation among years, permanent spatial variation
among groups of quadrats, and local neighborhood crowding from
conspecific and heterospecific genets. Regression coefficients for the
effect of crowding by each species can be considered a matrix of
interaction coefficients whose diagonals represent intraspecific
interactions and whose off-diagonals represent interspecific
interactions (Adler et al. 2010). These interaction coefficients can
take positive (facilitative) or negative (competitive) values. We
modeled growth as the change in size of a genet from one year to the
next, which depends on the same factors as the survival model. We fit
the survival and growth regressions using INLA (Rue et al. 2014), a
statistical package for fitting generalized linear mixed effects models
via approximate Bayesian inference (Rue et al. 2009), in R (R Core Team
2013). Spatial (quadrat groupings) variation was treated as a random
effect on the intercept and temporal (interannual) variation was treated
as random effects on the intercept and the effect of genet size in the
previous year (Appendix S1).

@@

Our study produced four main findings that were generally consistent
across five natural grassland plant communities: (1) limiting-case predictions
from the theoretical model were well-supported by simulations from the
empirical models; (2) demographic stochasticity decreased community
synchrony, as expected by theory, and its effect was largest in small
populations; (3) environmental fluctuations increased community
synchrony relative to simulations in constant environments because
species-specific responses to the environment were positively, though
not perfectly, correlated; and (4) interspecific interactions were weak
and therefore had little impact on community synchrony. We also found
that analyses based on synchrony of species' percent cover, rather than
growth rates, were uninformative (Figs. S2-S3) since the linear
approximation required for analytical predictions is a stronger
assumption for abundance than growth rates, especially given relatively
short time-series (Appendix S1). Thus, our results provide further
evidence that it is difficult to decipher mechanisms of species
synchrony from abundance time series, as expected by theory (Loreau and
{{de Mazancourt}} 2008). Observed synchrony of per capita growth rates
was positively correlated with the variability of percent cover across
our focal communities, which confirms that we are investigating an
important process underlying ecosystem stability.

@@

This work was funded by the National Science Foundation through a
Postdoctoral Research Fellowship in Biology to ATT (DBI-1400370) and a
CAREER award to PBA (DEB-1054040). CdM and ML were supported by the
TULIP Laboratory of Excellence (ANR-10-LABX-41). We thank the original
mappers of the permanent quadrats at each site and the digitizers in the
Adler lab, without whom this work would not have been possible. Compute,
storage, and other resources from the Division of Research Computing in
the Office of Research and Graduate Studies at Utah State University are
gratefully acknowledged. We also thank Patrick Venail and several
anonymous reviewers who provided critical feedback that improved the
manuscript.

@@

Plummer, M. 2003. JAGS: A Program for Analysis of Bayesian Graphical
Models Using Gibbs Sampling. Pages 20--22 \emph{in} Proceedings of the
3rd international workshop on distributed statistical computing (dSC
2003). march.

Plummer, M. 2014. rjags: Bayesian graphical models using MCMC.

R Core Team. 2013. R: A language and environment for statistical
computing.

@@

Rue, H., S. Martino, F. Lindgren, D. Simpson, A. Riebler, and E.
Teixeira. 2014. INLA: Functions which allow to perform full Bayesian
analysis of latent Gaussian models using Integrated Nested Laplace
Approximaxion.

@@

Tilman, D. 1988. Plant strategies and the dynamics and structure of
plant communities. Plant strategies and the dynamics and structure of
plant communities.:360 pp.

@@

Venail, P. A., M. A. Alexandrou, T. H. Oakley, and B. J. Cardinale.
2013. Shared ancestry influences community stability by altering
competitive interactions: evidence from a laboratory microcosm
experiment using freshwater green algae. Proceedings of the Royal
Society of London B: Biological Sciences 280.

@@

Wang, S., and M. Loreau. 2016. Biodiversity and ecosystem stability
across scales in metacommunities. Ecology Letters.

>>>>

%%\usepackage{lineno}
%%\linenumbers
\usepackage{todonotes}
\usepackage{rotating}
\usepackage{color, soul}
%\usepackage{times}
\usepackage[document]{ragged2e}
\usepackage{titlesec}
\titleformat{\section}{\normalsize\sc\centering}{\thesection}{1em}{}
\titleformat{\subsection}{\normalsize\it\centering}{\thesubsection}{1em}{}
\titleformat*{\paragraph}{\normalsize\it}
 \usepackage{bm,mathrsfs}
  \usepackage{mathptmx}

@@

\begin{center}
\Large{Environmental responses, not species interactions, determine synchrony of dominant species in semiarid grasslands}

@@

\begin{abstract}
\normalsize
\emph{Abstract.}\hspace{1em}Temporal asynchrony among species helps diversity to stabilize ecosystem functioning, but identifying the mechanisms that determine synchrony remains a challenge.
Here, we refine and test theory showing that synchrony depends on three factors: species responses to environmental variation, interspecific interactions, and demographic stochasticity. We then conduct simulation experiments with empirical population models to quantify the relative influence of these factors on the synchrony of dominant species in five semiarid grasslands.
We found that the average synchrony of per capita growth rates, which can range from 0 (perfect asynchrony) to 1 (perfect synchrony), was higher when environmental variation was present (0.62) rather than absent (0.43).
Removing interspecific interactions and demographic stochasticity had small effects on synchrony. 
For the dominant species in these plant communities, where species interactions and demographic stochasticity have little influence, synchrony reflects the covariance in species' responses to the environment.

@@

While existing theory has identified
environmental responses, species interactions, and demographic stochasticity as the drivers of the temporal synchrony,
we do not have a simple expression to predict synchrony in a particular
community with all factors operating simultaneously. However, we can
derive analytical predictions for species synchrony under special
limiting cases. The limiting case predictions we derive serve as
baselines to help us interpret results from empirically-based
simulations (see \textsc{Empirical Analysis}). We focus on synchrony of per capita
growth rates, rather than abundances, because growth rates represent the
instantaneous response of species to the environment and competition,
and are less susceptible to the legacy effects of drift and disturbance
(Loreau and {{de Mazancourt}} 2008). We present equivalent results for
synchrony of species abundances in the Appendix S1, and show that they
lead to the same overall conclusions as synchrony of per capita growth
rates.

@@

\noindent where \(\sigma_{r_{i}}\) is the temporal
standard deviation of species \emph{i'}s per capita
population growth rate (\(r_i\)) and \(\sigma^{2}_{T}\) is the temporal
variance of the aggregate community-level growth rate. \(\phi\) ranges
from 0 at perfect asynchrony to 1 at perfect synchrony (Loreau and {{de
Mazancourt}} 2008). We use the same equation to calculate observed
synchrony of species' percent cover, which we present to relate our
results to previous findings, even though we focus on synchrony of
growth rates in our model simulations (see \emph{Simulation experiments}).

@@

Vital rate regressions are the building blocks of our dynamic models: an
integral projection model (IPM) and an individual-based model (IBM). We
followed the approach of Chu and Adler (2015) to fit statistical models
for survival, growth, and recruitment (see Appendix S1 for full
details). We modeled survival probability of each genet as function of
genet size, temporal variation among years, permanent spatial variation
among groups of quadrats, and local neighborhood crowding from
conspecific and heterospecific genets. Regression coefficients for the
effect of crowding by each species can be considered a matrix of
interaction coefficients whose diagonals represent intraspecific
interactions and whose off-diagonals represent interspecific
interactions (Adler et al. 2010). These interaction coefficients can
take positive (facilitative) or negative (competitive) values. We
modeled growth as the change in size of a genet from one year to the
next, which depends on the same factors as the survival model. We fit
the survival and growth regressions using INLA (Rue et al. 2014), a
statistical package for fitting generalized linear mixed effects models
via approximate Bayesian inference (Rue et al. 2009), in R (R Core Team
2013). Spatial (quadrat groupings) variation was treated as a random
effect on the intercept and temporal (interannual) variation was treated
as random effects on both the intercept and the effect of genet size in the
previous year (Appendix S1).

@@

Our study produced four main findings that were generally consistent
across five natural grassland plant communities: (1) limiting-case predictions
from the theoretical model were well-supported by simulations from the
empirical models; (2) demographic stochasticity decreased community
synchrony, as expected by theory, and its effect was largest in small
populations; (3) environmental fluctuations increased community
synchrony relative to simulations in constant environments because
species-specific responses to the environment were positively, though
not perfectly, correlated; and (4) interspecific interactions were weak
and therefore had little impact on community synchrony. We also found
that analyses based on synchrony of species' percent cover, rather than
growth rates, were uninformative (Figs. S2-S3) since the linear
approximation required for analytical predictions is a stronger
assumption for abundance than growth rates, especially given relatively
short time-series (Appendix S1). Thus, our results provide further
evidence that it is difficult to decipher mechanisms of species
synchrony from abundance time series, as predicted by theory (Loreau and
{{de Mazancourt}} 2008). Observed synchrony of per capita growth rates
was positively correlated with the variability of percent cover across
our focal communities, which confirms that we are investigating an
important process underlying ecosystem stability.

@@

This work was funded by the National Science Foundation through a
Postdoctoral Research Fellowship in Biology to ATT (DBI-1400370) and a
CAREER award to PBA (DEB-1054040). CdM and ML were supported by the
TULIP Laboratory of Excellence (ANR-10-LABX-41) and by the BIOSTASES 
Advanced Grant, funded by the European Research Council under the European 
Union's Horizon 2020 research and innovation programme (grant agreement No 666971).
We thank the original
mappers of the permanent quadrats at each site and the digitizers in the
Adler lab, without whom this work would not have been possible. Compute,
storage, and other resources from the Division of Research Computing in
the Office of Research and Graduate Studies at Utah State University are
gratefully acknowledged. We also thank Patrick Venail and several
anonymous reviewers who provided critical feedback that improved the
manuscript.

@@

Plummer, M. 2003. JAGS: a program for analysis of Bayesian graphical models using Gibbs sampling. Proceedings of the Third International Workshop on Distributed Statistical Computing, 20?22 March 2003, Vienna, Austria. http://www.r-project.org/conferences/DSC-2003/Proceedings/Plummer.pdf

Plummer, M. 2014. rjags: Bayesian graphical models using MCMC. R package version 4-6. http://cran.r-project.org/package=rjags

R Core Team. 2013. R: A language and environment for statistical
computing. https://www.r-project.org/

@@

Rue, H., S. Martino, F. Lindgren, D. Simpson, A. Riebler, and E.
Teixeira. 2014. INLA: Functions which allow to perform full Bayesian
analysis of latent Gaussian models using Integrated Nested Laplace
Approximaxion. R package version 0.0-1483776432. http://www.r-inla.org/home.

@@

Tilman, D. 1988. Plant strategies and the dynamics and structure of
plant communities. Plant strategies and the dynamics and structure of
plant communities. Princeton University Press, Princeton, New Jersey.

@@

Venail, P. A., M. A. Alexandrou, T. H. Oakley, and B. J. Cardinale.
2013. Shared ancestry influences community stability by altering
competitive interactions: evidence from a laboratory microcosm
experiment using freshwater green algae. Proceedings of the Royal
Society of London B: Biological Sciences 280:20131548.

@@

Wang, S., and M. Loreau. 2016. Biodiversity and ecosystem stability
across scales in metacommunities. Ecology Letters 19:510--518.
